---
title: "Week 3 Homework: Titis in the Mist"
author: "Victoria Zdanowicz"
date: "9/23/2021"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
    toc_float: TRUE
---


Prompt - Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session.

<span style="color: red;">I really like the table of contents idea, it allows the reader to easily navigate between each challenge and also looks sleek</span>


# Challenge 1

> What is the probability that she will hear more than 8 calls during any given session?

This question requires the argument [lower = FALSE] to calculate the probability of more than 8 calls since it in the upper tail of the probability density function.

```{r 1}
x<- ppois(8, lambda=15, lower=FALSE)    
x
```
<span style="color: red;">I used lower.tail=F but both definitely work</span>

# Challenge 2

> What is the probability that she will hear no calls in a session?

Without the [lower = FALSE] argument, this command calculates the probability of zero or fewer calls in a session.   
```{r 2}
x<- ppois(0, lambda=15)    
x
```
<span style="color: red;">Once again we both get the same answer, but I used dpois since it didn't seem too relevant to get the probability of zero or FEWER calls.</span>

# Challenge 3

> What is the probability that she will hear exactly 3 calls in a session?

The function dpois() calculates the probability of a random variable, exact number of calls in this instance, that is available within a certain range.
```{r 3}
x<- dpois(3, lambda=15, log=FALSE) #if log = TRUE, probability is given as log
x
```
<span style="color: red;">I think log=FALSE is the default for dpois so it isn't necessarily needed but it is interesting to know that there is a log option</span>

# Challenge 4

> Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

I used a histogram to represent the Poisson distribution of the number of calls between 0 and 30. BARPLOT
```{r 4}
z<-dpois(0:30, lambda = 15)
plot(0:30, dpois(0:30, lambda = 15),
     type='h',
     main='Poisson Mass Function (lambda = 15)',
     ylab='Probability',
     xlab ='# Titi Calls',
     lwd=3)
```
<span style="color: red;">Your plot looks very nice! Definitely a step up from the standard mass function plot. The x access probabily doesn't need to clarify # and could probably just be "Titi Calls"</span>

# Challenge 5

> Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

The function rpois() is used for generating random numbers from a given Poisson’s distribution.
```{r 5}
y<-rpois(104,lambda=15)
y
hist(y,xlim=c(0,30),xlab="# Titi Calls",main="Simulated Call Histogram",breaks=30,col="darkslategray2")
```

Both histograms are similar in general shape/trend but the "Simulated Call Histogram" would likely appear  more similar to the "Poisson Mass Function" as more results are added to the sample size.

<span style="color: red;">I definitely like the color added! I think Chris talked about how there was a way for the R markdown to only use the same previously randomly generated sample so that it always looks the same? I think in future that might be beneficial so that the histogram always shows the same random distribution from the samples.</span>

<span style="color: red;">**Overall, this is awesome code! The added styles are a great addition, but you also explain what you are doing in a very detailed way that is easy to understand. Great work!**</span>



