---
title: "Week 3 Homework: Titis in the Mist"
author: "Victoria Zdanowicz"
date: "9/23/2021"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
    toc_float: TRUE
---

*Prompt - Every Saturday morning, at the same time, a primatologist goes and sits in the forest to listen for titi monkey calls, counting the number of calls they hear in a 2 hour window from 5am to 7am. Based on previous knowledge, she believes that the mean number of calls she will hear in that time is exactly 15. Let X represent the appropriate Poisson random variable of the number of calls heard in each monitoring session. *


### Challenge 1

> What is the probability that she will hear more than 8 calls during any given session?

This question requires the argument [lower = FALSE] to calculate the probability of more than 8 calls since it in the upper tail of the probability density function.
```{r 1}
library(manipulate) 
x<- ppois(8, lambda=15, lower=FALSE)    
x
```
 
### Challenge 2

> What is the probability that she will hear no calls in a session?

Without the [lower = FALSE] argument, this command calculates the probability of zero or fewer calls in a session.   
```{r 2}
x<- ppois(0, lambda=15)    
x
```
dpois() could also be used here to calculate the probability of exactly zero calls, ppois() can be used in this instance though because there cannot be fewer than zero calls. 
```{r}
x<- dpois(x=0, lambda = 15)
x
```

### Challenge 3

> What is the probability that she will hear exactly 3 calls in a session?

The function dpois() calculates the probability of a random variable, exact number of calls in this instance, that is available within a certain range.
```{r 3}
x<- dpois(3, lambda=15, log=FALSE) #if log = TRUE, probability is given as log
x
```

### Challenge 4

> Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

I used a histogram to represent the Poisson distribution of the number of calls between 0 and 30
```{r 4}
z<-dpois(0:30, lambda = 15)
plot(0:30, dpois(0:30, lambda = 15),
     type='h',
     main='Poisson Mass Function (lambda = 15)',
     ylab='Probability',
     xlab ='# Titi Calls',
     lwd=3)
```

### Challenge 5

> Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).
Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

The function rpois() is used for generating random numbers from a given Poisson’s distribution.
```{r 5}
y<-rpois(104,lambda=15)
y
hist(y,xlim=c(0,30),xlab="# Titi Calls",main="Simulated Call Histogram",breaks=c(0:30),col="darkslategray2")
```

Both histograms are similar in general shape/trend but the "Simulated Call Histogram" would likely appear more similar to the "Poisson Mass Function" as more results are added to the sample size.

### Overall challenges
1. I was first overwhelmed by the prompt because my knowledge of stats is very rusty. However, I overcame my hesitancy by googling Poisson distribution and how to represent it in R. I found some great websites that explained what exactly Poisson does and the various functions like ppois() and dpois(), which were essential to this assignment. 

2. My second challenge is related to researching about Poisson in R. I was unsure of the exact arguments to include but after some research and following through other examples, I had a pretty good idea when to use TRUE/FALSE in certain argument positions and what I needed to include to get the desired result.   

3. I don't fully understand all the potential arguments in hist(). I was unsure whether or not to include "breaks =" or if the y-axis to my last histogram was supposed to be frequency like how it is now, or probability like the Poisson Mass Function figure. 

4. I used a slightly different histogram style for Challenge 4, based on code I found online while researching Poisson Mass Functions. I was unsure if I should have used the same histogram from Challenge 5 and the modules or not. I think the one I used here is okay though because it still shows the same general shape/trend that is important to the questions at hand. It was helpful to try another plot style though and see how they look different and may have pros/cons in certain contexts depending on what you are trying to display. It is also fascinating to see how many different ways there are to do things!
